\begin{thebibliography}{1}

\bibitem{internet-pop}
    \emph{
    Internet Usage Statistics, The Internet Big Picture, World Internet Users
        and 2021 Population Stats
    }
    \\
    \color{gray}
Internetworldstats.com
    \\
    \color{black}
    \scriptsize{
        \url{
        https://www.internetworldstats.com/stats.htm
        }
}
\normalsize


\bibitem{noint}
    \emph{Facts and Figures 2021: 2.9 billion people still offline}
    \\
    \color{gray}
    International Telecommunication Union (ITU)
    \\
    \color{black}
    \scriptsize{
        \url{
https://www.itu.int/hub/2021/11/facts-and-figures-2021-2-9-billion-people-still-offline/
        }
    }
    \normalsize

\bibitem{google-stats}
\emph{Google Search Statistics}
\\
\color{gray}
Internet Live Stats
\\
\color{black}
\scriptsize{
    \url{
https://www.internetlivestats.com/google-search-statistics/
        }
}
\normalsize

\bibitem{prism}
\emph{
NSA Prism program taps into user data of Apple, Google and others.
}
\\
\color{gray}
Pulitzer.org
\\
\color{black}
\scriptsize{
    \url{
https://www.pulitzer.org/files/2014/public-service/guardianus/02guardianus2014.pdf
            }
}
\normalsize

\bibitem{guardian}
    \emph{
        The Guardian, a british daily newspaper.
    }
    \\
    \color{gray}
    Theguardian.com
    \\
    \color{black}
    \scriptsize{
        \url{
https://www.theguardian.com/us?INTCMP=CE_US
            }
    }
    \normalsize

\bibitem{pulitzer-guardian}
\emph{
    The 2014 Pulitzer Prize Winner in Public Service, The Guardian US.
}
\\
\color{gray}
Pulitzer.org
\\
\color{black}
\scriptsize{
    \url{
https://www.pulitzer.org/winners/guardian-us
            }
}
\normalsize

\bibitem{5-billion}
\emph{
    FTC’s \$5 billion Facebook settlement: Record-breaking and history-making.
}
\\
\color{gray}
    Federal Trade Commission
\\
\color{black}
\tiny{
    \url{
https://www.ftc.gov/news-events/blogs/business-blog/2019/07/ftcs-5-billion-facebook-settlement-record-breaking-history
            }
}
\normalsize

\bibitem{100-million}
\emph{
    Facebook to Pay \$100 Million for Misleading Investors About the Risks It
    Faced From Misuse of User Data
}
\\
\color{gray}
    US. Securities and Exchange Commission
\\
\color{black}
\scriptsize{
\url{
https://www.sec.gov/news/press-release/2019-140
            }
}
\normalsize

\bibitem{ieee-privacy}
\emph{
    User Data Privacy: Facebook, Cambridge Analytica, and Privacy Protection
}
\\
\color{gray}
J. Isaak and M. J. Hanna,\color{black}\ in Computer, vol. 51, no. 8, pp. 56-59,
August 2018, doi: 10.1109/MC.2018.3191268. Publisher: IEEE.
\\
\color{black}
\scriptsize{
    \url{
https://ieeexplore.ieee.org/abstract/document/8436400
            }
}
\normalsize

\bibitem{gdpr}
\emph{
    What is GDPR, the EU’s new data protection law?
    }
    \\
    \color{gray}
    Ben Wolford, Editor in Chief, GDPR EU
    \\
    \color{black}
    \scriptsize{
        \url{
            https://gdpr.eu/what-is-gdpr/?cn-reloaded=1
        }
    }
    \normalsize

\bibitem{use-2012}
    \emph{
        Search Engine Use 2012,
    } March 9, 2012,
    \\
    \color{gray}
        Kristen Purcell,
        Joanna Brenner,
        Lee Rainie,
    \\
    \color{black}
        Pew Research Center’s Internet \& American Life Project
    \\
    \scriptsize
        \url{
            https://www.ris.org/uploadi/editor/1341041853PIP_Search_Engine_Use_2012.pdf
        }
    \normalsize

\bibitem{Lucene}
\emph{
Welcome to Apache Lucene
}
\\
\color{gray}
Lucene.apache.org
\\
\color{black}
\scriptsize
\url{
https://lucene.apache.org/
        }
\normalsize

\bibitem{Typesense}
\emph{
Typesense's homepage
}
\\
\color{gray}
Typesense.org
\\
\color{black}
\scriptsize
\url{
https://typesense.org/
        }
\normalsize

\bibitem{duck}
\emph{
    The search page for DuckDuckGo.
}
\\
\color{gray}
    DuckDuckGo.com
    \\
    \color{black}
    \scriptsize
        \url{
            https://duckduckgo.com/
        }
    \normalsize

\bibitem{startpage}
    \emph{
    The search page for Startpage.
    }
    \\
    \color{gray}
    Startpage.com
    \\
    \color{black}
    \scriptsize
        \url{
            https://startpage.com/
        }
    \normalsize

\bibitem{duck-open}
    \emph{
    DuckDuckGo's Open-Source Areas
    }
    \\
    \color{gray}
    help.duckduckgo.com
    \\
    \color{black}
    \scriptsize
        \url{
            https://help.duckduckgo.com/duckduckgo-help-pages/open-source/opensource-overview/
        }
    \normalsize


\bibitem{duck-pop}
\emph{
    DuckDuckGo's Traffic
}
\\
\color{gray}
duckduckgo.com
\\
\color{black}
\scriptsize
\url{
https://duckduckgo.com/traffic
        }
\normalsize

\bibitem{google}
    \emph{
        The Anatomy of a Large-Scale Hypertextual Web Search Engine
    }
    \\
    \color{gray}
    Sergey Brin, Lawrence Page,
    \color{black}
        Stanford University
    \\
    \scriptsize
        \url{
            http://ilpubs.stanford.edu:8090/361/1/1998-8.pdf
        }
    \normalsize

\bibitem{searx}
    \emph{
    Welcome to searx
    }
    \\
    \color{gray}
    searx.github.io
    \\
    \color{black}
    \scriptsize
        \url{
            https://searx.github.io/searx/
        }
    \normalsize

\bibitem{python}
\emph{
    The Python programming language.
}
\\
\color{gray}
    Python.org
\\
\color{black}
\scriptsize
\url{
https://www.python.org/
}
\normalsize


\bibitem{AGPLv3}
\emph{
    GNU Affero General Public License
    }
    \\
    \color{gray}
    www.gnu.org
    \\
    \color{black}
    \scriptsize
        \url{
https://www.gnu.org/licenses/agpl-3.0.en.html
        }
    \normalsize

\bibitem{space}
\emph{
Searx online instances
}
\\
\color{gray}
The Searx Project
\\
\color{black}
\scriptsize
\url{
https://searx.space/
        }
\normalsize

\bibitem{captcha}
    \emph{
        What is CAPTCHA?
    }
    \\
    \color{gray}
    Google Workspace Admin Help
    \\
    \color{black}
    \scriptsize
    \url{
    https://support.google.com/a/answer/1217728?hl=en
    }
    \normalsize

\bibitem{filtron}
    \emph{
        Filtron,
        Reverse HTTP proxy to filter requests by different rules.
    }
    \\
    \color{gray}
    User asciimoo\color{black}, on Github
    \\
    \scriptsize
    \url{
        https://github.com/asciimoo/filtron
    }
    \normalsize

\bibitem{events}
\emph{
    Github issue thread that details events between Google-Searx.
    User sut12 opened this issue on Oct 12, 2016 · 138 comments
}
\\
\color{gray}
    "Google Captcha \#729"
\\
\color{black}
\scriptsize
\url{
https://github.com/searx/searx/issues/729
}
\normalsize


\bibitem{list-oecd}
\emph{
    List of OECD Member countries - Ratification of the Convention on the OECD
}
\\
\color{gray}
Oecd.org
\\
\color{black}
\scriptsize
\url{
https://www.oecd.org/about/document/ratification-oecd-convention.htm
}
\normalsize

\bibitem{oecd}
\emph{
    Measuring the Digital Transformation: A Roadmap for the Future
}
\\
\color{gray}
OECD (2019)\color{black},\ OECD Publishing. doi: 10.1787/9789264311992-en
\\
\scriptsize
Full book:
\tiny
\\
\url{
https://www.oecd-ilibrary.org/science-and-technology/measuring-the-digital-transformation_9789264311992-en
}
\\
\scriptsize
Summary:
\tiny
\\
\url{
https://www.oecd-ilibrary.org/sites/37044f2e-en/index.html?itemId=/content/component/37044f2e-en
}
\normalsize

\end{thebibliography}
